Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Clean up foil characteristics fig caption
Clean up paragraph about induction

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{figures/all_foils_re_dep}
\caption{Foil section characteristics computed by XFOIL for various $Re_c$.}
\label{fig:foil-Re-dep}
\end{figure}

@@

The relative blade velocity $U_\mathrm{rel}$ was calculated by vector addition
of the free stream velocity and the opposite of the blade tangential velocity.
Note that this neglects any induction or slowing of the free stream by the
turbine forces, which would be present in a momentum/streamtube model. Since~the
goal of this approach was not to predict absolute performance, but rather gain
insight into relative changes with $Re$, this method was deemed acceptable, as it
is extremely simple and fast to~compute.

>>>>

    \includegraphics[width=0.9\textwidth]{figures/all_foils_re_dep}

    \caption{Normalized maximum lift coefficient \textbf{(a)}, drag coefficient
        \textbf{(b)}, and lift-to-drag ratio \textbf{(c)} computed by XFOIL at
        various $Re_c$  for each profile.}

    \label{fig:foil-Re-dep}
\end{figure}

@@

The relative blade velocity $U_\mathrm{rel}$ was calculated by vector addition
of the free stream velocity and the opposite of the blade tangential velocity.
Note that this neglects any induction, i.e., slowing of the free stream by the
turbine forces, which would be present in a momentum/streamtube model. Since~the
goal of this approach was not to predict absolute performance, but rather to
gain insight into relative changes with $Re$, this method was deemed acceptable,
as it is extremely simple and fast to~compute.
